---
title: "Welcome to my blog!"
description: |
  Resources and topics I find inspiring regarding all sorts of fields and issues
base_url: https://vdilego.github.io/
author:
  - name: Vanessa di Lego
date: 2022-05-10
twitter:
  site: "@v_dilego"
  creator: "@v_dilego"
categories:
  - Introduction
  - Interests
output:
  distill::distill_article:
    self_contained: false
    toc: true
---





```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
IMAGES_PATH <- here::here(
    "_posts",
    "welcome_files")
```

```{r step-01-03-screenshot, fig.cap="The Death of Socrates. Source: The Met Museum, New York", echo=FALSE, out.extra="class=external", cache=TRUE}
knitr::include_graphics(path =
                            fs::path(IMAGES_PATH,
                                     "death_socrates.jpeg"))

```



Hello, and welcome to my blog!

## Introduction

In my series of posts, I will explore themes I find interesting, in the intersection of demography, social and medical sciences, mathematics, policy relevant issues and much more. This is a personal view and space to connect the dots and my ecclectic taste! A bit of literature, music and food will have some space too. After all, they are the spice of life. Hope you enjoy!

Follow me as well on [**my professional page**](http://www.wittgensteincentre.org/en/staff/member/di-lego.htm), [**github**](https://github.com/vdilego) and [**\@v_dilego**](https://twitter.com/v_dilego).


## Some R pain as well

I will also share some R pain trajectories and other nerdy enterprises. I have been exploring a lot the connections of [{xaringan}](https://github.com/yihui/xaringan) and other resources. 



--VDL

