---
title: "Welcome to my blog!"
description: |
  Resources and topics I find inspiring regarding all sorts of fields and issues
author:
  - name: Vanessa di Lego
    url: https://twitter.com/v_dilego
date: 2022-05-10
twitter:
  site: "@v_dilego"
  creator: "@v_dilego"
base_url: https://vdilego.github.io/
categories:
  - Introduction
  - Interests
output:
  distill::distill_article:
    self_contained: false
    toc: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r metathis, message=FALSE, warning=FALSE, include=FALSE}
library(metathis)
meta() %>%
  meta_name("github-repo" = "vdilego/vdilego.github.io") %>%
  meta_viewport() %>%
  meta_social(
    title = "Welcome to my blog!",
    url = "https://vdilego.github.io/posts/2022-05-10-welcome-to-my-blog/",
    image = "https://vdilego.github.io/posts/2022-05-10-welcome-to-my-blog/death_socrates.jpeg",
    image_alt = "The death of Socrates.Painting from the MET Museum",
    og_type = "website",
    og_author = c("di Lego","Vanessa"),
    twitter_card_type = "summary_large_image",
    twitter_creator = "@v_dilego"
  )
```

Hello, and welcome to my blog!

## Introduction

In my series of posts, I will explore themes I find interesting, in the intersection of demography, social and medical sciences, mathematics, policy relevant issues and much more. This is a personal view and space to connect the dots and my ecclectic taste! A bit of literature, music and food will have some space too. After all, they are the spice of life. Hope you enjoy!

Follow me as well on [**my professional page**](http://www.wittgensteincentre.org/en/staff/member/di-lego.htm), [**github**](https://github.com/vdilego) and [**\@v_dilego**](https://twitter.com/v_dilego).


## Some R pain as well

I will also share some R pain trajectories and other nerdy enterprises. I have been exploring a lot the connections of [{xaringan}](https://github.com/yihui/xaringan) and other resources. 



--VDL

