---
title: "Artificial Inteligence and Mathematical Intuition"
description: |
  Is it still mathematics when you use AI for guiding intuition?
author:
  - name: Vanessa di Lego
date: 2022-05-10
twitter:
  site: "@v_dilego"
  creator: "@v_dilego"
categories:
  - Mathematics
  - Artifical Inteligence
  - Intuition
  - Knowledge
  - Human
output:
  distill::distill_article:
    self_contained: false
    toc: true
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
IMAGES_PATH <- here::here(
    "_posts",
    "10May2022_files")
```

```{r step-01-03-screenshot, fig.cap="Knot Theory,Trefoil Knot. Source: Towards Data Science", echo=FALSE, out.extra="class=external", cache=TRUE}
knitr::include_graphics(path =
                            fs::path(IMAGES_PATH,
                                     "knot.gif"))

```



## Mathematics, Intuition and Artificial Inteligence 

In December 2021, a paper was published in [**Nature**](https://www.nature.com/articles/s41586-021-04086-x), showing how machine-learning tools can be used to guide the intuition of mathematicians. The paper particularly outlines a framework for how artificial inteligence and mathematicians can work together for advancing the field of pure mathematics and make powerful contributions to open problems. Two fields are particularly the focus of the paper: 1. the algebraic and geometric structure of knots and the combinatorial invariance conjecture for symmetric groups. The paper is quite interesting and it raises a lot of issues. One is concerned with the very field of mathematics and the concept of intuition. 

In fact, the role of computational power, data and programs is becoming important for all fields. It is definitely shaping how we are currently developing knowledge in the 21st Century. It is an important and fast shift. In demography, for instance, increased computer power has definitely enabled to advance so many topics and opened other research avenues. I often feel that we are more and more becoming data scientists and programming has become more essential for our everyday tasks. Use of different sources of data (cite monica nad diego) as well as big data have also inflood demographic reasearch.

However, as much as I value and consider this an important advancement, I cannot stop but wonder how will this shift shape the way we do, think and interpret research. In an area where we don´t have “cursed curves”, but “live curves”, how can we find a balance where knowledge is traceable? Who is held accountable for producing knowledge that often guides policy and informs important human phenomena? In order to have a brief but provocative discussion on this, we have to resort, as usual, to philosophy, and start asking some fundamental questions.

### What is Mathematics?

Let´s start first with what is Mathematics and how could the use of AI or machine learning tools affect the very concept of the field. 

### What is Intuition for Mathematicians?

A second important, and related question concerns the role of intuition for mathematicians. Intuition is a tricky concept and that is a topic on its own - maybe for another post : ). But for mathematicians it has a more specific concept - which is key. To approach the topic I will recover the very notion of proof and how mathematicians go about making proofs, so that we can dive into the topic in a more "practical way".

In one another part of my website I mention Kevin Buzzard on Proof and this talk at [**Collège de France**](https://www.college-de-france.fr/site/timothy-gowers/seminar-2021-11-15-14h00.htm) on November 15, 2021, [**Professor and Mathematician Kevin Buzzard**](https://www.imperial.ac.uk/people/k.buzzard) prompts the topic of "what is proof?", within the field of Philosophy of Mathematical Practice. This sets the tone for what actually is a mathematical proof. There are other problems that he mentions to take stock of the issue of proof itself as a scientific practice and its validity, especifically in a field where this is so essential such as mathematics. Another interesting topic he raises are the differences between human proof and computer proof. So how *do* mathematicians use their intuition?



### Is Mathematics still Mathematics when not "Human"?

Now this all raises the question of is Mathematics still Mathematics when not solely "human". Are we "humanizing" AI or is it mathematizing us? 


--VDL




